---
title: "628 pro1"
author: "Chenxi He, Yaqi Zhou, Wenxue Zhang"
date: "January 27, 2016"
output: html_document
---
## c.Code for analysis with documentation
```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(ggplot2)
library(zoo)
library(scales)
library(gtable)
library(grid)
library(vars)
library(fUnitRoots)
library(tseries)
library(dplyr)
library(lubridate)
setwd("~/Desktop/628")
```

```{r,warning=FALSE}
data <-read.csv("pro1-data.csv") # size=727

sum_ns <- data %>%
  group_by(Month,Year) %>%
  summarise(sum(ns)) %>%
  ungroup() %>%
  arrange(Year,Month)
colnames(sum_ns)[3]<-"ns_month"

# Two plots overlapped
draw <-function(p1,p2){
  # extract gtable
g1 <- ggplot_gtable(ggplot_build(p1))
g2 <- ggplot_gtable(ggplot_build(p2))
# overlap the panel of 2nd plot on that of 1st plot
pp <- c(subset(g1$layout, name == "panel", se = t:r))
g <- gtable_add_grob(g1, g2$grobs[[which(g2$layout$name == "panel")]], pp$t,pp$l, pp$b, pp$l)
# axis tweaks
ia <- which(g2$layout$name == "axis-l")
ga <- g2$grobs[[ia]]
ax <- ga$children[[2]]
ax$widths <- rev(ax$widths)
ax$grobs <- rev(ax$grobs)
ax$grobs[[1]]$x <- ax$grobs[[1]]$x - unit(1, "npc") + unit(0.15, "cm")
g <- gtable_add_cols(g, g2$widths[g2$layout[ia, ]$l], length(g$widths) - 1)
g <- gtable_add_grob(g, ax, pp$t, length(g$widths) - 1, pp$b)
ia <- which(g2$layout$name == "ylab")
ga <- g2$grobs[[ia]]
ga$rot <- 270
g <- gtable_add_cols(g, g2$widths[g2$layout[ia, ]$l], length(g$widths) - 1)
g <- gtable_add_grob(g, ga, pp$t, length(g$widths) - 1, pp$b)
return (g)
}

# Granger Test
monthly_granger=function(y=2013){
  dy=data[year(data$Date)==y,]
  p=c(1:12)
  for(i in 1:12){
    d=dy[month(dy$Date)==i,]
    air_sec <- data.frame(airindex=ts(d$log_daverage),stockret=ts(d$returns))
    xx=VARselect(air_sec,lag.max = 10,type = "both")
    xxx=as.numeric(xx$selection[1])
    vmodel<-VAR(air_sec,xxx,type = "both")
    x=causality(vmodel,cause = "airindex")
    p[i]=x$Instant$p.value
  }
  return(p)
}

# Monthly Granger for difference
monthly_granger=function(y=2013){
  dy=data[year(data$Date)==y,]
  p=c(1:12)
  for(i in 1:12){
    d=dy[month(dy$Date)==i,]
    air_sec <- data.frame(airindex=ts(d$log_daverage),stockret=ts(d$difference))
    xx=VARselect(air_sec,lag.max = 10,type = "both")
    xxx=as.numeric(xx$selection[1])
    vmodel<-VAR(air_sec,xxx,type = "both")
    x=causality(vmodel,cause = "airindex")
    p[i]=x$Instant$p.value
  }
  return(p)
}

# negative returns
data1<-data
data1$neg_returns<-(-data1$returns)
monthly_granger=function(y=2013){
  dy=data1[year(data$Date)==y,]
  p=c(1:12)
  for(i in 1:12){
    d=dy[month(dy$Date)==i,]
    air_sec <- data.frame(airindex=ts(d$neg_returns),stockret=ts(d$difference))
    vmodel<-VAR(air_sec,0,type = "both")
    x=causality(vmodel,cause = "airindex")
    p[i]=x$Instant$p.value
  }
  return(p)
}


month<-rep(1:12,3)
year<-rep(2013:2015,each=12)
p.value=c(monthly_granger(2013),monthly_granger(2014),monthly_granger(2015))
a<-data.frame(month=month,p.value=p.value,pollution=sum_ns$ns_month,year=year)
a$month<-as.factor(a$month)
ggplot(data=a,aes(x=month,y=p.value,size=pollution,color=pollution)) + geom_point() + geom_hline(yintercept=0.05,color="red") + ggtitle("Granger test results for each month") + facet_wrap(~year)

# two plots
sep13<-data[159:177,] # September 13
p1 <- ggplot(sep13) + geom_line(aes(Day, log_daverage,group=1),colour = "blue") + theme_bw() + ggtitle("Sep 13") 
p2 <- ggplot(sep13) + geom_line(aes(Day, returns, group=1),colour = "red") + geom_line(aes(Day, sp_returns, group=1),colour="green") + geom_line(aes(Day, difference, group=1),colour="black")+ theme_bw() %+replace%
    theme(panel.background = element_rect(fill = NA))
grid.newpage()
grid.draw(draw(p1,p2))

sep13<-data1[159:177,] # September 13 (negative returns)
p1 <- ggplot(sep13, aes(Day, log_daverage,group=1)) + geom_line(colour = "blue") + theme_bw() + ggtitle("Sep 13")
p2 <- ggplot(sep13, aes(Day, neg_returns, group=1)) + geom_line(colour = "red") + theme_bw() %+replace%
    theme(panel.background = element_rect(fill = NA))
grid.newpage()
grid.draw(draw(p1,p2))

mar13<-data[36:56,] # March 13
p1 <- ggplot(mar13, aes(Day, log_daverage,group=1)) + geom_line(colour = "blue") + theme_bw() + ggtitle("March 13")
p2 <- ggplot(mar13, aes(Day, returns,group=1)) + geom_line(colour = "red") + theme_bw() %+replace%
    theme(panel.background = element_rect(fill = NA))
grid.newpage()
grid.draw(draw(p1,p2))

mar13<-data[36:56,] # March 13
p1 <- ggplot(mar13, aes(Day, log_daverage,group=1)) + geom_line(colour = "blue") + theme_bw()
p2 <- ggplot(mar13, aes(Day, difference, group=1)) + geom_line(colour = "red") + theme_bw() %+replace%
    theme(panel.background = element_rect(fill = NA))
grid.newpage()
grid.draw(draw(p1,p2))

feb15<-data[504:518,] #Feb15
p1 <- ggplot(feb15, aes(Day, log_daverage,group=1)) + geom_line(colour = "blue") + theme_bw()
p2 <- ggplot(feb15, aes(Day, returns,group=1)) + geom_line(colour = "red") + theme_bw() %+replace%
    theme(panel.background = element_rect(fill = NA))
grid.newpage()
grid.draw(draw(p1,p2)) 

library(knitr)
Year<-c("2013","2014","2015")
ADFtest<-rep("stationary",3)
Lag<-c(1:3)
Granger<-c("significant","not significant","not significant")
b<-data.frame(Year,ADFtest,Lag,Granger)
kable(head(b),align="c") 

